\chapter{CHAPTER TITLE} \label{c4}
\section{Format for preparation of synopsis/thesis / dissertation}
The following sections describes how your thesis should be formatted according to standard guidelines.
\section{Synopsis}
Synopsis should be a condensed version of the thesis with a \textbf{maximum of 15 pages excluding references}.

\section{Sequencing}
The sequence in which the thesis should be arranged and bound should be as follows:
\begin{enumerate}\itemsep 0em
	\item Cover Page \& Title Page
	\item Declaration 
	\item Certificate
	\item Abstract (not exceeding 300 words)
	\item Acknowledgement (1 page)
	\item Table of Contents
	\item List of Figures / Exhibits / Charts 
	\item List of Tables 
	\item Symbols \& Notations
	\item Chapters
	\item Appendices
	\item References	
\end{enumerate}

\section{Page dimensions \& binding specifications}
The dimension for printing the thesis in bond sheet (Size A4) is as follows:

\subsection{Page specification}
\begin{table}[htb]
	\begin{tabular}{ll}
	Left Margin 		&: 1.5 inch \\
	Right Margin		&: 1 inch \\
	Top Margin		&: 1 inch \\
	Bottom Margin	&: 1 inch 
	
	\end{tabular}	
\end{table}

\subsection{Thesis binding}
The thesis should be bound using flexible cover (soft binding) for initial submission. The cover should be printed in black letters and the text for printing should be identical. After defensive viva, the thesis should be bound using rough surface rexin black cover printed in golden letters. The guidelines total number of pages in the report for each program
is shown below:
\begin{table}[htb]
\fontsize{10}{12}\selectfont
	\caption{Total Number of Pages in the Thesis}
	\begin{tabular}{|L{3cm}|L{2cm}|L{8cm}|}
		\hline
		\textbf{Course}	& \textbf{Color of Art Paper} & \textbf{Total Number of Pages in the Thesis} \\ \hline
		\textbf{Ph D} &	White &	Min. of 100 (Excluding References, Appendices and Front pages) \\\hline
		\textbf{M Phil / M.Tech [By Research]} & White & Min. of 80 - Max. of  200 (Excluding References, Appendices and Front pages) \\ \hline
	\end{tabular}	
\end{table}

\subsection{Printing standard}
\begin{table}[htb]
	\begin{tabular}{ll}
		For Initial Submission &: JK Bond Sheet \\
		For Final Submission &: Executive Bond Sheet
		
	\end{tabular}	
\end{table}

\section{Page numbers}
All text pages as well as program source code listings should be numbered using Arabic numerals at the bottom center of the pages.

\section{Font}
Times New Roman 12pt font should be used consistently throughout the text. Captions for tables and figures can be in smaller fonts, but not smaller than 10pt.

\section{Paragraphs} 
No paragraph should have its opening line at the bottom of a page. A clear, consistent, but not too large a separation must be provided between the paragraphs throughout the thesis. 

\section{Line spacing}
The line spacing used should be the same throughout the text, and can be chosen to be 1.5. The lines in captions for figures and tables, Table of Contents, List of Figures, and List of Tables should be 1.5 line spacing. 

\section{Headings}
\begin{table}[htb]
	\begin{tabular}{ll}
		Chapter Number & Font Size:  14,  Times New Roman, CAPS, bold \\
      Chapter Heading & Font Size: 16, Bold, Times New Roman, CAPS \\
      Section Heading & Font Size: 14, Times New Roman, Sentence Case \\
		Subsection Heading & Font Size: 12, Bold, Times New Roman, Sentence Case
	\end{tabular}	
\end{table}


	
	

